---
title: "Supplementary data - nucleoprotein structure" 
subtitle: "An evolutionary approach to identifying mammalian adaptive mutations in the avian influenza polymerase"
author: "Fernando Capelastegui, Vidhi Dholakia, Damien C. Tully, Daniel H. Goldhill"
output: html_document
---
<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>

H5N1 Nucleoprotein monomer (PDB:2Q06 - chain A) and H1N1 trimer structure (PDB:2IQH)

* Top 50 mutations observed by count. Colour gradient represents number of occurrences; the lighter the hue, the higher the count. 
* Mutations which were selected for experimental analysis. 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Results {.tabset}

### Monomer - Top 50 mutations (NP)

```{r, echo=FALSE, out.width="100%"}
np_model1_labels
```

### Monomer - Mutations selected for analysis (NP)

```{r, echo=FALSE, out.width="100%"}
np_model3
```


### Trimer - Top 50 mutations (NP)

```{r, echo=FALSE, out.width="100%"}
trimer1_labelled
```

### Trimer - Mutations selected for analysis (NP)

```{r, echo=FALSE, out.width="100%"}
trimer3
```

